A large-scale analysis of racial disparities in police stops across the United

### 2019-12-12 lib/paper_results.Rmd
minor paper and mj edits

```{r setup, echo = FALSE, message = FALSE, warning = FALSE}
source(here::here("lib", "utils.R"))
library(tidyverse)
library(knitr)
opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
pfs <- read_rds(here::here("results", "prima_facie_stats.rds"))
vod <- read_rds(here::here("results", "veil_of_darkness.rds"))
disp <- read_rds(here::here("results", "disparity.rds"))
mj <- read_rds(here::here("results", "marijuana_legalization_analysis.rds"))
```

@@

```{r search_rates}
tbl <- pfs$rates$search %>% 
  mutate(
    agency = if_else(city == "Statewide", "state patrol", "municipal pd"),
    var = search_rate * (1 - search_rate) / n
  ) %>% 
  group_by(agency, subject_race) %>%
  summarize(
    average_search_rate = mean(search_rate),
    std_error = sqrt(sum(var)) / n(),
    lower_ci = average_search_rate - 1.96 * std_error,
    upper_ci = average_search_rate + 1.96 * std_error
  ) %>%
  ungroup()
tbl %>% kable()
# TODO(danj): Make sure these make sense given new CI computations
ptbl <- tbl %>%
  mutate(
    n_success = average_n_searches,
    n_failure = average_n - average_n_searches
  )
pstate <- filter(ptbl, str_detect(agency, 'state'))
pcity <- filter(ptbl, str_detect(agency, 'municipal'))
```

Search p-values:
`r slice(pstate, 1:2) %>% select(agency, subject_race) %>% kable()`
p-value: `r slice(pstate, 1:2) %>% select(n_success, n_failure) %>% as.matrix %>% prop.test %$% p.value`
`r slice(pstate, -2) %>% select(agency, subject_race) %>% kable()`
p-value: `r slice(pstate, -2) %>% select(n_success, n_failure) %>% as.matrix %>% prop.test %$% p.value`
`r slice(pstate, 2:3) %>% select(agency, subject_race) %>% kable()`
p-value: `r slice(pstate, 2:3) %>% select(n_success, n_failure) %>% as.matrix %>% prop.test %$% p.value`
`r slice(pcity, 1:2) %>% select(agency, subject_race) %>% kable()`
p-value: `r slice(pcity, 1:2) %>% select(n_success, n_failure) %>% as.matrix %>% prop.test %$% p.value`
`r slice(pcity, -2) %>% select(agency, subject_race) %>% kable()`
p-value: `r slice(pcity, -2) %>% select(n_success, n_failure) %>% as.matrix %>% prop.test %$% p.value`
`r slice(pcity, 2:3) %>% select(agency, subject_race) %>% kable()`
p-value: `r slice(pcity, 2:3) %>% select(n_success, n_failure) %>% as.matrix %>% prop.test %$% p.value`

@@

```{r search_rates}
pfs$summary_table
```

@@

City and State outcomes:
```{r disparity-hit_rates-tables}
tbl <- rbind(
  disp$city$outcome$results$hit_rates %>% 
    group_by(geography, subject_race) %>% 
    summarize(
      hit_rate = weighted.mean(`contraband_found where search_conducted`, n_search_conducted),
      var = hit_rate * (1 - hit_rate) / sum(n_search_conducted)
    ) %>% 
    group_by(subject_race) %>% 
    summarize(
      geography = "cities",
      hit_rate = mean(hit_rate),
      std_error = sqrt(sum(var)) / n(),
      lower_ci = hit_rate - 1.96 * std_error,
      upper_ci = hit_rate + 1.96 * std_error
    ),
  disp$state$outcome$results$hit_rates %>% 
    group_by(geography, subject_race) %>% 
    summarize(
      hit_rate = weighted.mean(`contraband_found where search_conducted`, n_search_conducted),
      var = hit_rate * (1 - hit_rate) / sum(n_search_conducted)
    ) %>% 
    group_by(subject_race) %>% 
    summarize(
      geography = "states",
      hit_rate = mean(hit_rate),
      std_error = sqrt(sum(var)) / n(),
      lower_ci = hit_rate - 1.96 * std_error,
      upper_ci = hit_rate + 1.96 * std_error
    )
  ) %>% 
  select(geography, everything())
tbl %>% kable()
# TODO(danj): Make sure these make sense given new CI computations
ptbl <- tbl %>%
  mutate(
    n_success = average_n_contraband_found,
    n_failure = average_n_search_conducted - average_n_contraband_found
  )
pstate <- filter(ptbl, geography == "states")
pcity <- filter(ptbl, geography == "cities")
```

Hit rate p-values:
`r slice(pstate, 1:2) %>% select(agency, subject_race) %>% kable()`
p-value: `r slice(pstate, 1:2) %>% select(n_success, n_failure) %>% as.matrix %>% prop.test %$% p.value`
`r slice(pstate, -2) %>% select(agency, subject_race) %>% kable()`
p-value: `r slice(pstate, -2) %>% select(n_success, n_failure) %>% as.matrix %>% prop.test %$% p.value`
`r slice(pstate, 2:3) %>% select(agency, subject_race) %>% kable()`
p-value: `r slice(pstate, 2:3) %>% select(n_success, n_failure) %>% as.matrix %>% prop.test %$% p.value`
`r slice(pcity, 1:2) %>% select(agency, subject_race) %>% kable()`
p-value: `r slice(pcity, 1:2) %>% select(n_success, n_failure) %>% as.matrix %>% prop.test %$% p.value`
`r slice(pcity, -2) %>% select(agency, subject_race) %>% kable()`
p-value: `r slice(pcity, -2) %>% select(n_success, n_failure) %>% as.matrix %>% prop.test %$% p.value`
`r slice(pcity, 2:3) %>% select(agency, subject_race) %>% kable()`
p-value: `r slice(pcity, 2:3) %>% select(n_success, n_failure) %>% as.matrix %>% prop.test %$% p.value`

@@

@@

@@

```{r mj_treatment_search_rates_plot, fig.height=5, fig.width=10}
mj$plots$search_rates
```

@@

```{r mj_treatment_misdemeanor_rates_plot, fig.height=5, fig.width=10}
mj$plots$misdemeanor_rates
```

>>>>

```{r setup, echo = FALSE, message = FALSE, warning = FALSE}
source(here::here("lib", "utils.R"))
source(here::here("lib", "format_plots_for_paper.R"))
library(tidyverse)
library(patchwork)
library(knitr)
opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
pfs <- read_rds(here::here("results", "prima_facie_stats.rds"))
vod <- read_rds(here::here("results", "veil_of_darkness.rds"))
disp <- read_rds(here::here("results", "disparity.rds"))
mj <- read_rds(here::here("results", "marijuana_legalization_analysis.rds"))
mjf <- format_mj(mj)
```

@@

```{r search_rates_cis}
pfs$rates$search %>% 
mutate(
  agency = if_else(city == "Statewide", "state patrol", "municipal pd"),
  var = search_rate * (1 - search_rate) / n
) %>% 
group_by(agency, subject_race) %>%
summarize(
  average_search_rate = mean(search_rate),
  std_error = sqrt(sum(var)) / n(),
  lower_ci = average_search_rate - 1.96 * std_error,
  upper_ci = average_search_rate + 1.96 * std_error
) %>%
ungroup() %>%
kable()
```

@@

```{r search_rates_summary}
pfs$summary_table
```

@@

City and State outcomes:
```{r disparity-hit_rates-tables}
rbind(
disp$city$outcome$results$hit_rates %>% 
  group_by(geography, subject_race) %>% 
  summarize(
    hit_rate = weighted.mean(hit_rate, n_search_conducted),
    var = hit_rate * (1 - hit_rate) / sum(n_search_conducted)
  ) %>% 
  group_by(subject_race) %>% 
  summarize(
    geography = "cities",
    hit_rate = mean(hit_rate),
    std_error = sqrt(sum(var)) / n(),
    lower_ci = hit_rate - 1.96 * std_error,
    upper_ci = hit_rate + 1.96 * std_error
  ),
disp$state$outcome$results$hit_rates %>% 
  group_by(geography, subject_race) %>% 
  summarize(
    hit_rate = weighted.mean(hit_rate, n_search_conducted),
    var = hit_rate * (1 - hit_rate) / sum(n_search_conducted)
  ) %>% 
  group_by(subject_race) %>% 
  summarize(
    geography = "states",
    hit_rate = mean(hit_rate),
    std_error = sqrt(sum(var)) / n(),
    lower_ci = hit_rate - 1.96 * std_error,
    upper_ci = hit_rate + 1.96 * std_error
  )
) %>% 
select(geography, everything()) %>%
kable()
```
\newpage

@@

city then state

@@

\newpage
```{r mj_search_rates_treatment, fig.height=3, fig.width=8}
sr <- mj$plots$search_rates
mjf$treatment_search_rates
```

CO: `r sr$CO$count`

WA: `r sr$WA$count`

decrease:
```{r mj_decrease}
mjf$treatment_discretionary_searches_with_no_contraband %>%
kable()
```

@@

```{r mj_misdemeanor_rates_treatment, fig.height=3, fig.width=8}
md <- mj$plots$misdemeanor_rates
mjf$treatment_misdemeanor_rates
```

CO: `r md$CO$count`

WA: `r md$WA$count`

@@

```{r mj_search_rates_control, fig.height=5.75, fig.width=10}
mjf$control_search_rates
```
AZ: `r sr$AZ$count`

CA: `r sr$CA$count`

FL: `r sr$FL$count`

MA: `r sr$MA$count`

MT: `r sr$MT$count`

NC: `r sr$NC$count`

OH: `r sr$OH$count`

RI: `r sr$RI$count`

SC: `r sr$SC$count`

TX: `r sr$TX$count`

VT: `r sr$VT$count`

WI: `r sr$WI$count`
